SMASH companion source code repository

### 2018-12-20 analysis/index.Rmd
wflow_publish("index.Rmd")

+ The `output` directory contains results from the Gaussian and
  Poisson simulations.

@@

Our numerical comparisons also use of some functions from
[waveden][waveden], so we have included the GaussianWaveDen source in
this repository. For information about distributing GaussianWaveDen,
see the `copyright.m` in the WavDen subdirectory. Note that we made
one small improvement to the code in `blockJS.m` to prevent an error
that occurs when running the code in newer versions of MATLAB.

>>>>

+ The `output` directory contains results from the Gaussian and
  Poisson simulations. File `pois_hf.RData` contains results from
  experimenting with different Gaussian denoising techniques for the
  Haar-Fisz algorithm in the Poisson simulations.

@@

Our numerical comparisons also use of some functions from
[GaussianWaveDen][waveden], so we have included the GaussianWaveDen
source in this repository. For information about distributing
GaussianWaveDen, see the `copyright.m` in the WavDen
subdirectory. Note that we made one small improvement to the code in
`blockJS.m` to prevent an error that occurs when running the code in
newer versions of MATLAB.
